Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex
first attempt at formalizing the privacy properties

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
  identities must be unlinkable to their proofs.
\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
  unlinkable between protests and witnesses' proofs must be unlinkable between 
  protesters.
\end{requirements}

As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
This is, in fact, is a slight increase in privacy over ordinary protests.

>>>>

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
  participant's real (long-term) 
  identity (\(P\)) must be unlinkable to their participation proofs $\prf_{\pid, \prtst}$
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
  participation proofs $\prf_{\pid, \prtst}$ must be 
  unlinkable between protests ($\cid, \cid'$)
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
  participation proof shares $\(\psh = (\cid, t, l, \pid, \wid)\)$ must be unlinkable between 
  protesters. ($\pid, \pid'$)
\end{requirements}

\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
This is, in fact, is a slight increase in privacy over ordinary protests.}
